CSCI 447: Project 1

### 2019-09-13 paper/paper.tex
DANA PUT HERE

\subsection{Separating and classifying data}
To properly implement naive Bayes [3] on the 5 data sets, we first needed to properly separate and classify each data set. Each data set needed to be separated by class, and then the count and probability of each attribute value for each class needed to be computed. Our approach for this was to create, for each dataset, an associative array, where each possible classifier was a key. For each key, the corresponding values were each their own associative arrays, the keys of which were all the extant attribute values among that class. The value of each key in these inner arrays was a set storing the count and conditional probability of each attribute value given the respective class. \\ \\

@@

\subsection{Loss function 2: 0-1 Loss}
-TODO: describe Loss function in a similar function to precision recall.

\section{Results}

\section{Conclusions}
\subsection{Breast Cancer Wisconsin}
\subsection{Glass}
\subsection{Iris}
\begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
    \centering
    \begin{minipage}[b]{0.7\textwidth}
      \includegraphics[width=\textwidth]{01_loss_graph.png}
      \caption{Average 0/1 Loss for \emph{Iris} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.4\textwidth}
      \includegraphics[width=\textwidth]{precision_graph.png}
      \caption{Average Precision for \emph{Iris} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.4\textwidth}
        \includegraphics[width=\textwidth]{recall_graph.png}
        \caption{Average Recall for \emph{Iris} (over 1,000 iterations)}
    \end{minipage}
\end{figure}

@@

\subsection{Soybean}
\subsection{Voting Records}

>>>>

\subsection{Separating and classifying data}
To properly implement naive Bayes [3] on the 5 data sets, we first needed to properly separate and classify each data set. Each data set needed to be separated by class, and then the count and probability of each attribute value for each class needed to be computed. Our approach for this was to create, for each data set, an associative array, where each possible classifier was a key. For each key, the corresponding values were each their own associative arrays, the keys of which were all the extant attribute values among that class. The value of each key in these inner arrays was a set storing the count and conditional probability of each attribute value given the respective class. \\ \\

@@

\subsection{Loss function 2: 0-1 Loss}
-TODO: describe Loss function in a similar function to precision recall.
TODO: DANA PUT HERE

\section{Results}
TODO: DANA PUT HERE

\section{Conclusions}

\subsection{Breast Cancer Wisconsin}

\begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
    \centering
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{bc-l-ms.png}
        \includegraphics[width=\textwidth]{bc-l-ds.png}
        \caption{Average difference between 0/1 Loss for normal data set and noise data set for \emph{Breast Cancer Wisconsin} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{bc-p-ms.png}
        \includegraphics[width=\textwidth]{bc-l-ds.png}
        \caption{Average difference between Precision for normal data set and noise data set for\emph{Breast Cancer Wisconsin} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{bc-r-ms.png}
        \includegraphics[width=\textwidth]{bc-r-ds.png}
        \caption{Average difference between Recall for normal data set and noise data set for \emph{Breast Cancer Wisconsin} (over 1,000 iterations)}
    \end{minipage}
\end{figure}

\subsection{Glass}

\begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
    \centering
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{g-l-ms.png}
        \includegraphics[width=\textwidth]{g-l-ds.png}
        \caption{Average difference between 0/1 Loss for normal data set and noise data set for \emph{Glass} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{g-p-ms.png}
        \includegraphics[width=\textwidth]{g-l-ds.png}
        \caption{Average difference between Precision for normal data set and noise data set for\emph{Glass} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{g-r-ms.png}
        \includegraphics[width=\textwidth]{g-r-ds.png}
        \caption{Average difference between Recall for normal data set and noise data set for \emph{Glass} (over 1,000 iterations)}
    \end{minipage}
\end{figure}

\subsection{Iris}
\begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
    \centering
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{iris-loss-ms.png}
        \includegraphics[width=\textwidth]{densityfunc-iris-loss.png}
        \caption{Average difference between 0/1 Loss for normal data set and noise data set for \emph{Iris} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{iris-precs-ms.png}
        \includegraphics[width=\textwidth]{densityfunction-iris-precision.png}
        \caption{Average difference between Precision for normal data set and noise data set for\emph{Iris} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{iris-recall-ms.png}
        \includegraphics[width=\textwidth]{densityfunc-iris-recall.png}
        \caption{Average difference between Recall for normal data set and noise data set for \emph{Iris} (over 1,000 iterations)}
    \end{minipage}
\end{figure}

@@

\subsection{Soybean}

\begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
    \centering
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{soybean-l-ms.png}
        \includegraphics[width=\textwidth]{soybean-l-df.png}
        \caption{Average difference between 0/1 Loss for normal data set and noise data set for \emph{Soybean} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{soybean-p-ms.png}
        \includegraphics[width=\textwidth]{soybean-l-df.png}
        \caption{Average difference between Precision for normal data set and noise data set for\emph{Soybean} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{soybean-r-ms.png}
        \includegraphics[width=\textwidth]{soybean-r-df.png}
        \caption{Average difference between Recall for normal data set and noise data set for \emph{Soybean} (over 1,000 iterations)}
    \end{minipage}
\end{figure}

\subsection{Voting Records}

\begin{figure}[!hbp] % Credit to stack exchange user Masroor and user Stefan Kottwitz for the implementation of side by side figures in LaTeX
    \centering
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{vr-l-ms.png}
        \includegraphics[width=\textwidth]{vr-l-df.png}
        \caption{Average difference between 0/1 Loss for normal data set and noise data set for \emph{Voting Records} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{vr-p-ms.png}
        \includegraphics[width=\textwidth]{vr-p-df.png}
        \caption{Average difference between Precision for normal data set and noise data set for\emph{Voting Records} (over 1,000 iterations)}
    \end{minipage}
    \hfill
    \begin{minipage}[b]{0.3\textwidth}
        \includegraphics[width=\textwidth]{vr-r-ms.png}
        \includegraphics[width=\textwidth]{vr-r-df.png}
        \caption{Average difference between Recall for normal data set and noise data set for \emph{Voting Records} (over 1,000 iterations)}
    \end{minipage}
\end{figure}
